\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Islam Sabyrgaliyev}} & Email : \href{mailto:islam.sabyrgaliyev@gmail.com}{islam.sabyrgaliyev@gmail.com}\\
  \href{https://github.com/isabyr/}{https://github.com/isabyr/} & Mobile : +7-701-952-4782 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {BI Group}{Astana, Kazakhstan}
      {Software Engineer}{Feb 2019 - Present \vspace{6pt}}{some text\vspace{-6pt}}
      \resumeItemListStart
        \resumeItem{Smart Home}
          {Development of Smart Home Infrastructure using Home Assistant software stack. }
        \resumeItem{OpenThread}
          {Researching OpenThread capabilities with NRF52840}
      \resumeItemListEnd
    \resumeSubheading
      {CVT LLP}{Astana, Kazakhstan}
      {Senior Software/DevOps Engineer}{Aug 2017 - Apr 2018 \vspace{6pt}}
      {The company develops software for detecting traffic misdemeanors using computer vision and machine learning techniques. Responsibilities and accomplished tasks:\vspace{-6pt}}
      \resumeItemListStart
        \resumeItem{FFMpeg/CUDA}
          {Modifying FFmpeg library to extract additional data from video stream, like frame timestamp, packet loss rate. Implement Python2 interface for this library.}
        \resumeItem{DevOps}
          {Develop architecture for automated software deployment using Docker and Ansible AWX(Tower).}
        \resumeItem{Monitoring}
          {Configure logging system, reports: Fluentd, ElasticSearch, Kibana.}
        \resumeItem{System Administration}
          {Administering distributed compute nodes with GTX1050 GPU cards(up to 50).}
      \resumeItemListEnd
    \resumeSubheading
      {Nazarbayev University}{Astana, Kazakhstan}
      {Junior Researcher}{Nov 2019 - Jan 2017 \vspace{6pt}}
      {I was part of computer science laboratory. Projects involved in:\vspace{-6pt}}
      \resumeItemListStart
        \resumeItem{Assembling Kazakh Language Corpus}
          {The project is aimed at building the first kazakh language corpus as an initial step for development of language processing tools, such as morpho- and syntactic parsers. The project tasks include maintaining website(http://kazcorpus.kz) and developing web-based text annotation tool. Skills: Apache HTTP, Tomcat, Lucene, JSP/Servlet, JavaScript/jQuery.}
        \resumeItem{Designing cloud computing-based systems for Big Data}
          {The main goal of the project was to deploy a cloud platform to provide a versatile computing tools for research groups. I was responsible for the platform design, Openstack software setup and administering cloud portal(user support, computation tools setup). Skills: Linux, LXC, KVM, OpenStack, LDAP, Hadoop, Spark, MPI.}
      \resumeItemListEnd
    \resumeSubheading
      {Bee Software}{Astana, Kazakhstan}
      {Software Engineer}{Dec 2010 - Feb 2012 \vspace{6pt}}
      {The company builds large scale software systems for the government. There I participated in development of call center service for the Department of Justice. Key feature of the project was integrating Asterisk PBX to application server to manage VoIP functionality from the business process. Skills: Asterisk, VoIP, JBoss Seam, jBPM, PostgreSQL.}
%      \resumeItemListStart
%        \resumeItem{Call Center}
%        {The company builds large scale software systems for the government. There I participated in development of call center service for the Department of Justice. Key feature of the project was integrating Asterisk PBX to application server to manage VoIP functionality from the business process. Skills: Asterisk, VoIP, JBoss Seam, jBPM, PostgreSQL.}
%      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Freelance Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{KAMAZ}
      {Self driving KAMAZ truck at NU.}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubItem{SciNet}
      {Developed a website for scientific mentoring service(http://scinet.kz) using VueJS, Django REST, PostgreSQL.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Suleyman Demirel University}{Almaty, Kazakhstan}
      {Bachelor in Computing Systems and Software}{Sept. 2006 -- Jun. 2010}
  \resumeSubHeadingListEnd
\end{document}
